Tight Bounds for Dynamic Balanced Graph Partitioning

### 2020-05-11 paper/disc20clustering.tex
Comments

With each repartitioning,
\PPL moves to a component respecting partition that minimizes the distance to the initial partition $P_I$.
As a result,
\PPL never moves to a~partition that is more than $\Delta^*$  node migrations away from $P_I$.
This invariant latter ensures us that \PPL does not pay too much while recovering $P_F$.
We emphasize that a repartitioning by \PPL replaces the current partition $P$ with a~perfect partition closest to $P_I$.
Meaning, it never moves to a partition beyond the distance $\Delta^*$.

@@

>>>>

With each repartitioning,
\PPL moves to a component respecting partition that minimizes the distance to the initial partition $P_I$.
As a result,
\PPL never moves to a~partition that is more than $\Delta^*$  node migrations away from $P_I$.
This invariant latter ensures us that \PPL does not pay too much while recovering $P_F$.
We emphasize that a repartitioning by \PPL replaces the current partition $P$ with a~perfect partition closest to $P_I$.
This way \PPL never moves to a partition beyond the distance $\Delta^*$.

@@

\maciek{OPT's font differ from other proofs. We don't want italic OPT in mathenv}

\maciek{I really think that minimums should be expanded earlier than in the competitive ratio. The ratio should be bounded easily, and if you wish, you can emphasize the choice in the paragraph, or dedicate entire line to the cost expression. }
